% !TEX root = EIRSAT_ADCS_Model.tex

\section{Introduction}
This document details a study of the modelling and simulation of the Attitide Determination and Control System (ADCS) for the EIRSAT-1 cubesat.
This includes the satellite attitude dynamics, orbit propagation after release from the ISS; disturbances torques, position and attitude sensor models, magnetic actuator models and attitude feedback control system.
The simulation environment was developed using MATLAB/Simulink.
Simulation results are presented for several different test cases.
These test cases include demonstrations of different control modes, different control systems and different actuator and sensor configurations including failure of one or more devices.

\section{Objectives}
\begin{itemize} 
\item Create a simulation environment for the EIRSAT-1 ADCS subsystem including:
\begin{itemize} 
\item Satellite attitude dynamics, modelled as a single rigid body with 6DOF
\item Orbit propagation of the satellite after release from the ISS
\item Disturbance torques including: gravity gradient, solar radiation pressure, aerodynamic, residual magnetic field
\item orbit propagation after release from ISS
\end{itemize}
\item Define the different ADCS operational modes and functional requirements for each mode
\item Design feedback controllers for each mode of the ADCS:
\begin{itemize} 
\item first assuming ideal 3-axis actuators
\item then with two magnetorquer actuators
\end{itemize}
\item Design algorithm for safely switching between control modes
\item Design controllers for failure modes including:
\begin{itemize} 
\item failure of one magnetorquer
\item failure of attitude sensors (needs to be more clearly defined)
\end{itemize}
\end{itemize} 

\section{ADCS Modes and Functional Requirements}

\begin{itemize}
\item Detumbling
\item Sun/object pointing
\item Nadir/zenith pointing
\end{itemize}

\subsection{Detumbling} %Joe
Max rate to detumble?
Time taken to detumble?
Power?

\subsection{Sun/distant object pointing} % Victor
Required pointing accuracy?
Settling time from one place to another?
Power?

\subsection{Nadir/zenith pointing} % Daire
Required pointing accuracy?
Time?
Power?

\subsection{Switching between modes} % Joe
Which switches can happen?
When can they happen ? (where in orbit, in eclipse?)
Time taken?

