% !TeX root = EIRSAT_ADCS_Model.tex

\section{Spherical Harmonics}

The set of shperical harmonics is an orthonormal set of functions defined in the unit sphere. They are given as the angular part of the solution to the Laplace Equation in spherical coordinates. Here, it is important to identify the coordinates to be used, as, for instance, spherical coordinates have often two different interpretations, one, which is mainly used by physicist, uses the latitude [...] as one of the angular coordinates, while the other, 

Here, the spherical coordinates are taken to be
\begin{itemize} 
\item[] $r$, the radial distance from Earth's center
\item[] $\phi$, the East longitude % Bounded between... % ...write nicer
\item[] $\theta$, the co-latitude, defined to be $\theta = \frac{\pi}{2} - \theta'$, with $\theta'$ the latitude. % Bounded between... % ...write nicer
\end{itemize}


The magnetic field is given by the negative gradient of the potential $V$ defined for $r \geq R_e$, and given by the spherical harmonic approximation

\begin{equation} \label{eq:igrf_potential}
V = r \sum_{n=1}^{L} \left(\dfrac{R_e}{r}\right)^{n+1} \sum_{m=0}^{n} \left(g_n^m cos(m\phi) + h_n^m sin(m\phi)\right) P_n^m(cos\theta)
\end{equation}

That is
\begin{equation}
{\bm \beta} = -\nabla V
\end{equation}


Where $g_n^m$ and $h_n^m$ are the set of IGRF gaussian coefficients, published and revised every five years by the participating members of the IAGA (International Association
of Geomagnetism and Aeronomy). The $12^{th}$ generation is here used, as the last revision by the time of this work. These coefficient also include the secular variation (SV), which bestow the model on the proper time dependence.

$P_n^m(cos \theta)$ are the Schmidt normalized associated Legendree polynomials of degree n and order m

One can find very effective, recursive ways of computing the Schmidt quasi-normalization factors, the Associated Legendre polynomials and its derivatives, as can be found on [J.Davis - Mathematical Modeling of Earth’s Magnetic Field] %\cite{...}

The three componentens of the magnetic field in $r$, $\phi$ and $\theta$ directions can be found in terms of the partial derivatives of \ref{eq:igrf_potential}

\begin{equation}
{\bm \beta}_r = -\dfrac{\partial V}{\partial r} = \sum_{n=1}^{N} (n+1) \left(\dfrac{R_e}{r}\right)^{n+2} \sum_{m=0}^{n} \left(g_n^m cos(m\phi) + h_n^m sin(m\phi)\right) P_n^m(cos\theta)
\end{equation}

\begin{equation}
{\bm \beta}_{\theta} = -\dfrac{1}{r} \dfrac{\partial V}{\partial \theta} = 
-\sum_{n=1}^{L} \left(\dfrac{R_e}{r}\right)^{n+2} \sum_{m=0}^{n} \left(g_n^m cos(m\phi) + h_n^m sin(m\phi)\right) \dfrac{\partial P_n^m(cos\theta)}{\partial \theta}
\end{equation}

\begin{equation}
{\bm \beta}_{\theta} = -\dfrac{1}{r sin\theta} \dfrac{\partial V}{\partial \phi} = 
\dfrac{1}{sin\phi}\sum_{n=1}^{L} \left(\dfrac{R_e}{r}\right)^{n+2} \sum_{m=0}^{n} m\left(g_n^m sin(m\phi) - h_n^m cos(m\phi)\right) P_n^m(cos\theta)
\end{equation}

{\bf Legendre Polynomials}

The set of regular Legendre Polynomials is given by the solutions $P_n(\nu)$ to the equation
\begin{equation}
\dfrac{1}{\sqrt{1-2\nu x + x^2}} = \sum_{n=0}^\infty x^2 P_n(\nu)
\end{equation}
Which gives
\begin{equation}
P_n(\nu) = \dfrac{1}{n! 2^n} \dfrac{d^n}{d\nu^n} (\nu^2 -1)^n
\end{equation}

{\bf Associated Legendre Polynomials}

The associated Legendre polynomials $P_n^m(\nu)$ of degree n and order m relate to $P_n(\nu)$ by
\begin{equation}
P_{n,m}(\nu) = (1-\nu^2)^{\frac{1}{2m}} \dfrac{d^m}{d\nu^m}(P_n(\nu))
\end{equation}
These polynomias are not normalized in any way. 

{\bf Gaussian normalization and Schmidt quasi-normalization}

To compute the geomagnetic field, the Schmidt quasi-normalization is used, and is given by
\begin{equation}
P_n^m(\nu) = \sqrt{\dfrac{2(n-m)!}{(n+m)!}} P_{n,m}(\nu) 
\end{equation}

The Gaussian normalizalized Legendre polynomials, whose interest lies in the existence of a recursive formula for their effective computation are given by
\begin{equation}
P^{n,m}(\nu) = \dfrac{2^n! (n-m)!}{(2n)!} P_{n,m}(\nu)
\end{equation}

One can relate the Gaussian normalization and the Schmidt quasi-normalization by using
\begin{equation}
P_n^m(\nu) = \Gamma_{n,m} P^{n,m}(\nu)
\end{equation}
Where
\begin{equation}
\begin{aligned}
\Gamma_{n,m} &= \sqrt{\dfrac{(n-m)!}{(n+m)!}}\dfrac{(2n-1)!!}{(n-m)!}, &m = 0\\
\Gamma_{n,m} &= \sqrt{\dfrac{2(n-m)!}{(n+m)!}}\dfrac{(2n-1)!!}{(n-m)!}, &m \neq 0
\end{aligned}
\end{equation}

It is more convinient to modify the coefficients, as
\begin{equation}
\begin{aligned}
g_n^m &= \Gamma_{n,m}\ g_{n,m}\\ h_n^m &= \Gamma_{n,m}\ h_{n,m}
\end{aligned}
\end{equation}


\footnote{Note the use of notation here to distinguish between Regular, Associated, and Schmidt quasi-normalized Legendre Polynomials}

